\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{geometry}
\geometry{left=1cm,right=1cm}
\begin{document}

\part{Junjie Guan (Jack)}

\begin{multicols}{2}

\personal
    [www.gjjhomepage.sinaapp.com]
    {1 Sanborn Rd., Hanover, NH}
    {+1 (603) 277 1196}
    {gjj@cs.dartmouth.edu}

\section{Interested field}
Networking, Cloud, Distributed Computing, Web Design, Web Development


\section{Education}

\begin{yearlist}

\item[Computer Science, M.S.]{2013 -- 2015}
     {Dartmouth College}
     %{Hanover, US}

\item[Communication Engineering, , B.S.]{2009 -- 2012}
     {Beijing University of Posts and Telecommunication}
     %{Seminario vescovile, Cremona}

\end{yearlist}

\end{multicols}















\section{Professional Experience}

\begin{eventlist}

\item{Sep 2013 -- Present}
     {Software Developer @ Tiltfactor, Dartmouth}
     {Metadata Game Project}
     
     \quad1) developing and testing a full-stack website on Yii framework, help database design;
     
     \quad2) Cooperation with other programers around the world using Asana and Git.
     
     Granted from National Endowment for the Humanities (NEH), a open source, internet‐based system for augmenting access to archival records.
     
     
\item{Sep 2012 -- Feb 2013}
     {Research Assistant @ NetLab, Tsinghua University}
     {DCloud: Deadline Guaranteed Cloud Computing}
     
     \quad1) Design a new datacenter resource allocation mechanism, by considering deadline into job scheduling
     
     \quad2) Build thousands of lines of C++ simulations program
     
     \quad3) Implementation on a 16-machine cluster, writing controling  program with Python and Bash shell
     
     \quad4) Validating efficiency with Hadoop application using Java, 
     
     \quad5) Try compare with optimal solution using IBM Cplex.

     Increase job throughput by 30$\scriptsize{\sim}$50\% comparing to state-of-art, submitted to ACM SIGCOMM 2013.
     
\item{Aug 2011 -- Jul 2012}
     {Research Assistant @ Innovation Project Center of BUPT}
     {SIDES: Scalable Intelligent Distributed Emergency System}
     
     \quad1) Propose the idea of a decentralized self-organize wireless-based emergency system that generates real-time evaucation strategy to save lives in fire harzard, 
     
     \quad2) Design the the distributed protocol.
     
     \quad3) Conduct simulation on C++ program, and implement in Zigbee wireless nodes using C.
     
Shorten evacuation by 50\% comparing to normal strategy, Won first prize as National Class Innovation Project.

Publication: \textbf{Guan, Junjie}, et al. "SIDES: Scalable Intelligent Distributed Emergency System." Network Infrastructure and Digital Content (IC-NIDC), 2012 3rd IEEE International Conference on. IEEE, 2012.     
     
\end{eventlist}





















\section{Project in Competition}
\begin{eventlist}

\item{Dec 2011 -- May 2012}
     {Team Leader @ Microsoft Imagine Cup 2012}
     {UpAround Social Platform}
     
     \quad1) Propose the idea of a location-based social platform, and initiate a technique team of 4.
     
     \quad2) Manage the product development and presentation.
     
     \quad3) As lead programmer, built a full-stack social platform on .Net framework. 
     
     \quad4) Design and develop a highly-interactive UI using javascript/jQuery, html5, css3.
     
Gained the 3rd prize in Software Design China Zone (6\%).   

Youtube Url: \underline{http://goo.gl/jwzWQq}
       
\end{eventlist}

















\section{Independent work}


\begin{eventlist}

\item{2012 Summer}
     {Undergraduate @ Future Network Lab of BUPT}
     {Status-Based Content Sharing Mechanism for CCN}
     
	Reduce overheads and increase transfer rate by aournd 30\% in Content-Centric Network by pre-determining a host based on source status. Then built a experiment network based on CCNx using C. 

Publication: \textbf{Guan, Junjie}, et al. "Status-Based Content Sharing Mechanism for Content-Centric Network." Communication Technology (ICCT), 2012 IEEE 14th International Conference on. IEEE, 2012. 

\item{Apr 2011 -- May 2011}
     {Undergraduate @ Internet Research Department Center of BUPT}
     {WAP Topology Property Analysis: Comparison With WWW}     
     
\quad1) Developed a multi-thread web crawler using Python. 

\quad2) Keep recording statistics for weeks using mySql. 

\quad3) Analyzed the topology characteristics of WAP ,e.g. degree distribution and clustering coefficient.\newline

\end{eventlist}






















\if
\section{Professional skills}

\begin{factlist}

\item{Good level}
     {C++, Html(5), CSS(3), Javascript, jQuery, \LaTeX, Photoshop, Matlab}

\item{Intermediate}
     {Git, Python, Java, PHP, C\#, Bash shell script, MySQL, SqlServer, IBM Cplex Optimizer, Wireshark, AutoIt, Hadoop}

\item{Basic level}
     {Nodejs, Assembly, VHDL, NS2}

\end{factlist}

\fi











\end{document}
