\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{geometry}
\geometry{left=1cm,right=1cm}
\begin{document}

\part{Junjie Guan (Jack)}

\begin{multicols}{2}

\personal
    [https://github.com/jack2684]
    {Dartmouth College, 6211 Hinman}
    {+1 (603) 277 1196}
    {gjj@cs.dartmouth.edu}

\section{Interested field}
Networking, Distributed Computing, \newline Web Design, Web Development


\section{Education}

\begin{yearlist}

\item[Computer Science, M.S.]{2013 -- 2015}
     {Dartmouth College}
     %{Hanover, US}

\item[Communication Engineering, , B.S.]{2009 -- 2012}
     {Beijing University of Posts and Telecommunication}
     %{Seminario vescovile, Cremona}

\end{yearlist}

\end{multicols}















\section{Professional Experience}

\begin{eventlist}

\item{Jun 2014 -- Aug 2014}
     {SDE Intern @ Amazon AWS}
     {Builder Tools, Package Builder Services}
     
     \quad1) Implement the Auto-Unprune feature to relief customer from tedious manual procedure. 
     
     \quad2) Implement pacakge build history API as strech project.

\item{Mar 2014 -- Present}
     {Senior developer @ Dali Lab}
     {ArtxChange}
     
     \quad1) Implement the bussiness logic, including the customer roles, access control, art gallery and partner system.
     
     \quad2) Develop plugins such as the meta data export plugin
     \\\\
     A marketplace that connect artists, buyers and non-profit organzaions. Artists sell artwork while also fundraises for innovative, socially beneficial projects, which is beneficial to both artist and the society.

\item{Sep 2013 -- Mar 2014}
     {Software Developer @ Tiltfactor, Dartmouth}
     {Metadata Project}
     
     \quad1) Develop full-stack games (i.g, StupidRobot), and collect meta data from user's input.
     
     \quad2) Develop plugins such as the meta data export plugin
     
     \quad3) Fix any issue listed in bug tracker (Asana). Cooperation with other programers around the world using Git.
     \\\\
     Granted from National Endowment for the Humanities (NEH), a open source, internet‐based system for augmenting access to archival records.
	
      Url: \underline{http://www.metadatagames.org/}

      Repo:  \underline{https://github.com/jack2684/mg-game}

     
     
\item{Sep 2012 -- Feb 2013}
     {Research Assistant @ NetLab, Tsinghua University}
     {DCloud: Deadline Guaranteed Cloud Computing}
     
     \quad1) Design a new datacenter resource allocation mechanism, by considering deadline into job scheduling;
     
     \quad2) Build thousands of lines of C++ simulations program;
     
     \quad3) Implementation on a 16-machine cluster, writing controling  program with Python and Bash shell;
     
     \quad4) Validating efficiency with Hadoop application using; Java, 
     
     \quad5) Try compare with optimal solution using IBM Cplex;
	\\\\
     Increase job throughput by 30$\scriptsize{\sim}$50\% comparing to state-of-art, submitted to ACM SIGCOMM 2013.
     
     \quad A related former project where I contribute publication: Publication: Dan Li, Jing Zhu, Jianping Wu, \textbf{Junjie, Guan}, Guaranteeing Heterogeneous Bandwidth Demand in Multi-tenant Data Center Networks, accepted by IEEE/ACM Transactions on Networking ‘2014
     
     
     
     
     
     
     
     
     
     
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    










\clearpage
\item{Aug 2011 -- Jul 2012}
     {Research Assistant @ Innovation Project Center of BUPT}
     {SIDES: Scalable Intelligent Distributed Emergency System}
     
     \quad1) Propose the idea of a decentralized self-organize wireless-based emergency system that generates real-time evaucation strategy to save lives in fire harzard, 
     
     \quad2) Design the the distributed protocol.
     
     \quad3) Conduct simulation on C++ program, and implement in Zigbee wireless nodes using C.
     
Shorten evacuation by 50\% comparing to normal strategy, Won first prize as National Class Innovation Project.
\\\\
Publication: \textbf{Junjie, Guan}, Yanyi Wu, Jinming Ma, Tao Li, Chunlei Xie, Yuli Mo SIDES: Scalable Intelligent Distributed Emergency System, accepted by IC-NIDC’2012
     
\end{eventlist}





















\section{Project in Competition}
\begin{eventlist}

\item{Dec 2011 -- May 2012}
     {Team Leader @ Microsoft Imagine Cup 2012}
     {UpAround Social Platform}
     
     \quad1) Proposed the idea of a location-based social platform, and initiated a technique team of four.
     
     \quad2) Manage the product development and presentation.
     
     \quad3) As lead programmer, built a full-stack social platform on .Net framework. 
     
     \quad4) Design and develop a highly-interactive UI using javascript/jQuery, html5 and css3.
     \\\\
Gained the 3rd prize in Software Design China Zone (6\%).   

Youtube Url: \underline{http://goo.gl/jwzWQq}
       
\end{eventlist}

















\section{Other work}


\begin{eventlist}

\item{Summer 2012}
     {Undergraduate @ Future Network Lab of BUPT}
     {Status-Based Content Sharing Mechanism for CCN}
     
	Reduce overheads and increase transfer rate by aournd 30\% in Content-Centric Network by pre-determining a host based on source status. Then built a experiment network based on CCNx using C. 
\\\\
Publication: \textbf{Junjie, Guan}, Xudong Wang, Yu Xia, Tao Huang, Liang Wei Status-Based Content Sharing Mechanism for Content-centric Network, accepted by ICCT’2012

\item{Apr 2011 -- May 2011}
     {Undergraduate @ Internet Research Department Center of BUPT}
     {WAP Topology Property Analysis: Comparison With WWW}     
     
\quad1) Developed a multi-thread web crawler using Python. 

\quad2) Keep recording statistics for weeks using mySql. 

\quad3) Analyzed the topology characteristics of WAP, e.g. degree distribution and clustering coefficient.\newline

\end{eventlist}






















\if
\section{Professional skills}

\begin{factlist}

\item{Good level}
     {C++, Html(5), CSS(3), Javascript, jQuery, \LaTeX, Photoshop, Matlab}

\item{Intermediate}
     {Git, Python, Java, PHP, C\#, Bash shell script, MySQL, SqlServer, IBM Cplex Optimizer, Wireshark, AutoIt, Hadoop}

\item{Basic level}
     {Nodejs, Assembly, VHDL, NS2}

\end{factlist}

\fi











\end{document}
